Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-14 krs-survey.tex
Section on physics based reasoning

To the extend of our knowledge, no previous published work attempted to identify
knowledge-bound cognitive abilities required by service robotics.

@@

In~\cite{McCarthy2007}, McCarthy recently listed the challenges he identifies
on the road to a \emph{human-level AI}.

@@

We have detailed an imaginary cooking scenario where numerous desirable
features for a knowledge representation system for robotics have been
identified in no particular order.

@@

@@

>>>>

To the extend of our knowledge, no previous published work attempt to build a
typology of cognitive abilities related to knowledge and required by service
robotics.

@@

For instance, in~\cite{McCarthy2007}, McCarthy recently listed the challenges
he identifies on the road to a \emph{human-level AI}.

@@

We presented an imaginary cooking scenario where numerous desirable
features for a knowledge representation system for robotics have been
identified in no particular order.

@@

As embodied entities, robots have to interact with physical entities.
\emph{Naive physics reasoning} covers all the everyday reasoning the humans
unconsciouly perform, like taking into account gravity (``if I drop a ball, it
falls down'') or common physical properties of objects (``a glass may break if
dropped'', etc.). Many of the interactions with our everyday environments are
ruled by such laws that are difficult to exhaustively encode.

Some systems \cite{Kunze??} rely on external dedicated physics engine to
compute symbolic facts from on-demand physics simulation. This, however,
requires a tight integration between the symbolic model and a geometric model
that carries the geometries and physical properties of objects.

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{l|ccccccccc}
\hiderowcolors

{} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMKRF} & {\sc DY-KNOW} \\

\hline
\showrowcolors
{\bf Expressiveness} & & & & & & & & &  \\
Formal Logic & Prolog & OWL-DL & {\sc CycL} &  &  &  & & & \\
OWA/CWA & CWA & OWA & & & & & & & \\
Modeling uncertainty & +++ (add-on) & & & & & & & & \\
Meta-cognition & ++ & ++ & & & & & & & \\
{\bf Model} & & & & & & & & &  \\
{\bf Reasoning} & & & & & & & & &  \\
Standard FOL reasoning & +++ & +++ & & & & & & &  \\
Lazy evaluation & +++ & & & & & & & &  \\
Reasoning under uncertainty & ++ (add-on) & & & & & & & & \\
Non-monotonic reasoning & & & & & & & & &  \\
Presupposition accomodation & & & & & & & +++ & &  \\
Prediction, projection, diagnosis & & & & & & & & &  \\
Physics-based reasoning & +++ (add-on) & & & & & & & &  \\
Planning & + & +++ (external module) & & & & & & &  \\
Knowledge structure alteration & & ++ & & & & & & &  \\
Learning & & & & & & & & &  \\
{\bf Knowledge Acquisition} & & & & & & & & &  \\
{\bf Integration} & & & & & & & & &  \\
{\bf Knowledge Instanciation} & & & & & & & & &  \\
\hline

%\end{tabularx}
\end{tabular}
\end{center}
\caption{Main domain of contribution of each surveyed systems. Rating goes from +++ (major focus) to + (secondary interest). An empty cell means that 
the system does not consider this domain.}
\label{table|contribution-by-systems}
\end{table}
\end{landscape}
